---
title: "Extracting FARS Information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extracting FARS Information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(farsRP)
```

# Extracting FARS Information
Before using the functions, the FARS file should be installed in the working 
directory in the format accident_YEAR.csv.bz2, where YEAR is the correponding 
year. The data can be found in the [NHTSA website](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).

## Summarizing data from many years
To show the amount of fatalities in each month of one or many years the fars_summarize_years function can be used. It receives a vector containing the years that will be presented in the summary and returns a table with the amount 
of accidents each month.
```{r}
# Amount of fatalities per month in the years of 2014 and 2015.
fars_summarize_years(c(2014, 2015))
```

## Plotting data for a specific state and year
The fars_map_state plots the location of the fatalities in the selected state 
map for a specific year.
```{r}
# The location of the fatalities in the state of code 1 and the year of 2014.
fars_map_state(1, 2014)
```
